Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-28 paper.qmd
small changes to headers

#### Error calculation

@@

### pbmc
<!--
- NLDR view used to illustrate clusters
- Use our method to assess is it a reasonable representation
- Demonstrate that it is not
- Illustrate how to use our method to get a better representation
-->

@@

### digits: 1
<!--
- NLDR is used to illustrate different ways 1's are drawn
- Use our method to assess is it a reasonable representation
- Demonstrate that it is, except for the anomalies 
-->

>>>>

#### Residuals and error

@@

### Single-cell gene expression
<!--
- NLDR view used to illustrate clusters
- Use our method to assess is it a reasonable representation
- Demonstrate that it is not
- Illustrate how to use our method to get a better representation
-->

@@

### Hand-written digits
<!--
- NLDR is used to illustrate different ways 1's are drawn
- Use our method to assess is it a reasonable representation
- Demonstrate that it is, except for the anomalies 
-->
